---
title: "Week 6 Coding Lesson- Intro to Linear Regression"
author: "Laurel Wee"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```
Note: See lab 6 key for full descriptions

# Part 1: Attach Packages in setup chunk

# Part 2: A rank-based test example (Mann Whitney U)
```{r}
set.seed(1414) # to create a "pseudo-random" sample 
gp_1 <- sample.int(20, size = 15, replace = TRUE) # create sample vectors, use 'sample.int' to create random samples with integers from 1 to x, of size=?, and with replacement

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)

# quick look at a histogram

hist(gp_1)
hist(gp_2)
```

Rank-based test
Choose rank-based test because not normally distributed from exploratory histograms, small sample size, and ranks or median are more valuable metrics to compare this data. 

Will perform a Mann- Whitney u to answer
Is there a significant difference in ranks (medians)

```{r}
my_mwn <- wilcox.test(gp_1, gp_2)
my_mwn
```

# Part 3: Simple linear regression
## A. Look at palmer penguin data

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_point()
```
Looks like a linear relationship between flipper length and body mass makes sense. 

## B. Model it
Make model first then can check assumptions for linear regression that are based on model residuals (e.g. normality & homoscedasticity of residuals)

```{r}
# Linear model, stored as penguin_lm
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

# Return the complete overview
summary(penguin_lm)
```

## C. Access model outputs
```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm) # summary would be messy so use 'broom::tidy()'
```
```{r}
# Get the intercept:
penguin_int <-penguin_lm_tidy$estimate[1]
penguin_int
```
```{r}
# Then to get the flipper_length coefficient:
penguin_coef <-penguin_lm_tidy$estimate[2]
penguin_coef
```
```{r}
# Metrics at a glance
penguin_lm_out <- broom::tidy(penguin_lm)
penguin_lm_out
```
Example conclusion: “Simple linear regression was used to explore the relationship between penguin flipper length (mm) and body mass (g) across all three penguin species, and including both male and female penguins. A significant regression model was found (β = 49.686, F(1,340) = 1070.7, p < 0.001) with an R2 of 0.759.”

## D. Explore model assumptions

Explore assumptions for linear regression
- Linearly related variables (CHECK - already looked & thought hard)
- Normally distributed residuals
- Homoscedasticity (constant residuals variance)
- iid residuals (no serial correlation) - more often a concern in time series data

```{r}
plot(penguin_lm) # will automatically create four useful visualizations to consider assumptions
```
## E. Visualize the model
```{r}
ggplot(data = penguins, 
       aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point(size = 2) +
  geom_smooth(method = "lm", # to add a linear model to an existing scatterplot
              color = "red",
              size = 0.5,
              fill = "gray10",
              alpha = 0.5) +
  theme_light() +
  ggpubr::stat_regline_equation(label.x = 180, label.y = 5700) # to add equation information directly to the plot panel, x- and y- position that you specify
```


## F. Find Pearson's r for correlation:
```{r}
penguins_cor <- cor.test( # reports the r value and performs hypothesis test with null the correlation = 0
  penguins$flipper_length_mm, penguins$body_mass_g) # two vectors
```
Here, we see that there is a strong positive correlation between penguin flipper length and body mass (r = 0.87, t(340) = 32.72, p < 0.001).

# END of LAB
