---
title: "Week 6 Coding Lesson- Intro to Linear Regression"
author: "Laurel Wee"
date: "11/17/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

Part 1: Attach Packages in setup chunk

Part 2: A rank-based test example (Mann Whitney U)
```{r}
set.seed(1414) # to create a "pseudo-random" sample 
gp_1 <- sample.int(20, size = 15, replace = TRUE) # create sample vectors, use 'sample.int' to create random samples with integers from 1 to x, of size=?, and with replacement

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)

# quick look at a histogram

hist(gp_1)
hist(gp_2)
```

Rank-based test
Choose rank-based test because not normally distributed from exploratory histograms, small sample size, and ranks or median are more valuable metrics to compare this data. 

Will perform a Mann- Whitney u to answer
Is there a significant difference in ranks (medians)

```{r}
my_mwn <- wilcox.test(gp_1, gp_2)
my_mwn
```

Part 3: Simple linear regression
A. Look at palmer penguin data

```{r}
ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g))+
  geom_point()
```
Looks like a linear relationship between flipper length and body mass makes sense. 

B. Model it
Make model first then can check assumptions for linear regression that are based on model residuals (e.g. normality & homoscedasticity of residuals)

```{r}
# Linear model, stored as penguin_lm
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)

# Return the complete overview
summary(penguin_lm)
```

C. Access model outputs
```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm) # summary would be messy so use 'broom::tidy()'
```
```{r}
# Get the intercept:
penguin_int <-penguin_lm_tidy$estimate[1]
penguin_int
```
```{r}
# Then to get the flipper_length coefficient:
penguin_coef <-penguin_lm_tidy$estimate[2]
penguin_coef
```


